---
title: "Allie's First Repo"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
library(dplyr)
library(fivethirtyeight)
library(lubridate)
```

## GitHub Documents :D

This is an **R Markdown** _format_ used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r}
weekly_campaign_stops <- pres_2016_trail %>% 
  mutate(week = floor_date(date, unit = "week")) %>% 
  group_by(candidate, week) %>% 
  summarize(number_of_stops = n())
```

## Including Plots
# This is a plot

You can also embed plots, for example:

```{r pressure, echo=FALSE}
ggplot(data = weekly_campaign_stops, mapping = aes(x = week, y = number_of_stops, fill = candidate)) +
  geom_col() +
  ggtitle("Weekly stops during the 2016 presidential election")
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

# :]
